A Gaussian process model of human electrocorticographic data

### 2020-02-24 paper/main.tex
completed next pass through, updated stats from TM and LLWO

\section*{Approach} The SuperEEG approach to inferring high temporal resolution
full-brain activity patterns is outlined and summarized in
Figure~\ref{fig:methods}. We describe (in this section) and evaluate (in
\textit{Results}) our approach using a two large previously collected datasets
comprising multi-session intracranial recordings. Dataset 1 comprises
multi-session recordings taken from 6876 electrodes implanted in the brains of
88 epilepsy patients~\citep{SedeEtal03, SedeEtal07a, SedeEtal07b, MannEtal11,
MannEtal12}.  Each recording session lasted from 0.2--3~h (total recording time:
0.3--14.2~h; Fig.~\suppstats E).  During each recording session, the patients
participated in a free recall list learning task, which lasted for up to
approximately 1~h.  In addition, the recordings included ``buffer'' time (the
length varied by patient) before and after each experimental session, during
which the patients went about their regular hospital activities (confined to
their hospital room, and primarily in bed).  These additional activities
included interactions with medical staff and family, watching television,
reading, and other similar activities.  For the purposes of the Dataset 1
analyses presented here, we aggregated all data across each recording session,
including recordings taken during the main experimental task as well as during
non-experimental time.  We used Dataset 1 to develop our main SuperEEG approach,
and to examine the extent to which SuperEEG might be able to generate
task-general predictions.  Dataset 2 comprised multi-session recordings from
4436 electrodes implanted in the brains of 40 epilepsy
patients~\citep{EzzyEtal17, HoraEtal17, KragEtal17, KuceEtal17, LinEtal17,
SoloEtal18, WeidEtal18, EzzyEtal18, KuceEtal18}.  Each recording session lasted
from 0.4--2.2~h (total recording time: 0.4--6.6~h; Fig.~\suppstats K).  Whereas
Dataset 1 included recordings taken as the patients participated in a variety of
activities, Dataset 2 included recordings taken as each patient performed each
of two specific experimental memory tasks: a random word list free recall task
(Experiment 1) and a categorized word list free recall task (Experiment 2).  We
used Dataset 2 to further examine the ability of SuperEEG to generalize its
predictions within versus across tasks.  Figure~\suppstats~provides additional
information about both datasets.

@@

We first applied fourth order Butterworth notch filter to remove 60 Hz ($\pm$ .5
Hz) line noise from every recording (from every electrode). Next, we downsampled
the recordings (regardless of the original sample rate) to 250 Hz.  (This
downsampling step served to both normalize for differences in sampling rates
across patients and to ease the computational burden of our subsequent
analyses.)  We then excluded any electrodes that showed putative epileptiform
activity. Specifically, we excluded from further analysis any electrode that
exhibited a maximum kurtosis of 10 or greater across all of that patient's
recording sessions.  We also excluded any patients with fewer than 2 electrodes
that passed this criteria, as the SuperEEG algorithm requires measuring
correlations between 2 or more electrodes from each patient.  For Dataset 1,
this yielded clean recordings from 4168 electrodes implanted throughout the
brains of 67 patients (Fig.~\ref{fig:methods}A, colored dots); for Dataset 2,
this yielded clean recordings from 5023 electrodes implanted in 78 patients.
Each individual patient contributed electrodes from a limited set of brain
locations, which we localized in a common space~\citep[MNI152;][]{GrabEtal06};
an example Dataset 1 patient's 54 electrodes that survived the kurtosis
thresholding procedure are highlighted in black and red
(Fig.~\ref{fig:methods}A).

@@

We designed our approach to be agnostic to electrode impedances, as electrodes
that do not exist do not have impedances.  Therefore our algorithm recovers
voltages in standard deviation ($z$-scored) units rather than attempting to
recover absolute voltages. (This property reflects the fact that
$\hat{K}_{\beta_s, \alpha_s}$ and $\hat{K}_{\alpha_s, \alpha_s}$ are correlation
matrices rather than covariance matrices.)  Also, we note that
Equation~\ref{eqn:reconstruction} requires computing a $T$ by $T$ matrix, which
can become computationally intractable when $T$ is very large (e.g., an example
patient in Dataset 1, $T = 12,786,750$; also see Fig.~\suppstats, Panels E and
K). However, because Equation~\ref{eqn:reconstruction} is time invariant, we may
compute $Y_{s,k,\beta_s}$ in a piecewise manner by filling in $Y_{s,k,\beta_s}$
one row at a time (using the corresponding samples from $Y_{s, k, \alpha_s}$).

@@

%correlations by brain area, distribution of correlations
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/corrmap}
  \caption{\textbf{Reconstruction quality across all electrodes in two
      ECoG datasets.}  \textbf{A. Distributions of correlations
      between observed versus reconstructed activity by electrode, for
      Dataset 1.}  The across-patient distribution (black) reflects
    reconstruction accuracy (correlation) using a correlation model
    learned from all but one patient's data, and then applied to that
    held-out patient's data.  The within-patient distribution (gray)
    reflects performance using a correlation model learned from the same
    patient who contributed the to-be-reconstructed electrode.
    \textbf{B. Distributions of correlations for Dataset 2.}  This
    panel is in the same format as Panel A, but reflects results
    obtained from Dataset 2.  The histograms aggregate data across
    both Dataset 2 experiments; for results broken down by experiment
    see Figure~\perexptaskreconseparated. \textbf{C.--D.  Reconstruction
      performance by location.} The colors denote the average across-session
    correlation, using the across-patient correlation model, between
    the observed and reconstructed activity at the given electrode
    location projected to the cortical surface~\citep{CombEtal19}.}
  \label{fig:corrmap}
\end{figure}

@@

Although both datasets we examined provide good full-brain coverage (when
considering data from every patient; e.g.\ Fig.~\ref{fig:corrmap}C, D),
electrodes were not sampled uniformly throughout the brain.  For example,
electrodes are more likely to be implanted in regions like the medial temporal
lobe (MTL), and are rarely implanted in occipital cortex
(Fig.~\ref{fig:density}A, B). Separately for each dataset, for each voxel in the
4~mm$^3$ voxel MNI152 brain, we computed the proportion of electrodes in the
dataset that were contained within a 20 MNI unit radius sphere centered on that
voxel.  We defined the \textit{density} at that location as this proportion.
Across Datasets 1 and 2, the electrode placement densities were similar
(correlation by voxel: $r = 0.6, p < 10^{-10}$).  We wondered whether regions
with good covererage might be associated with better reconstruction accuracy.
For example, Figures~\ref{fig:corrmap}C and D indicate that many electrodes in
the MTL (which tends to be relatively densely sampled) have relatively high
reconstruction accuracy, and occipital electrodes (which tends to be relatively
sparsely sampled) tend to have relatively low reconstruction accuracy.  To test
whether this held more generally across the entire brain, for each dataset we
computed the electrode placement density for each electrode from each patient
(using the proportion of \textit{other} patients' electrodes within 20 MNI units
of the given electrode).  We then correlated these density values with the
across-patient reconstruction accuracies for eachg electrode.  We found a
statistically reliable negative correlation between reconstruction accuracy and
density for Dataset 1, but no reliable correlation for Dataset 2 (Dataset 1: $r
= -0.21, p = 0.05$; Dataset 2: $r = -0.30, p = 0.15$).  This indicates that the
reconstruction accuracies we observed are \textit{not} driven solely by sampling
density, but rather may also reflect higher order properties of neural dynamics
such as functional correlations between distant voxels~\citep{BetzEtal17b}.

Prior work in humans and animals has shown that the spatial profile of the local
field potential differs by frequency band~\citep[e.g., with respect to volume
conductance properties and contribution to the local field
potential;][]{BuzsEtal12, FrieEtal07, CronEtal11}.  For example, lower frequency
components of the local field potential tend to have higher power and extend
further in space than high-frequency components~\citep[e.g., ][]{MillEtal07,
MannEtal09}.  We therefore wondered whether the reconstructions we observed
might be differently weighting or considering the contributions of activity at
different frequency bands.  We therefore examined a range of frequency bands
($\delta$: 2--4 Hz; $\theta$: 4--8 Hz; $\alpha$: 8--12 Hz; $\beta$: 12--30 Hz;
$\gamma_L$: 30--60 Hz; and $\gamma_H$: 60--100 Hz), along with a measure of
broadband power~\citep[defined as the mean height of a linear robust regression
fit in log-log space to the order 4 Morelet wavelet-computed power spectrum at
50 log-spaced frequencies from from 2--100 Hz;][]{MannEtal09}.  We used
second-order Butterworth bandpass filters to compute the activity patterns
within each narrow frequency band.  We then repeated our within-subject and
across-subject cross-validated reconstruction accuracy tests (analogous to
Fig.~\ref{fig:corrmap}) separately for each frequency band
(Fig.~\ref{fig:frequency}).  (We also carried out a similar analysis on the
Hilbert transform-computed spectral power within each narrow band; see
Fig.~\freqpower.)  Across both datasets, we found that our approach is best at
reconstructing patterns of broadband activity (right-most bars in
Figs.~\ref{fig:frequency}A and D), a correlate of population firing
rate~\citep{MannEtal09}.  We also achieved good reconstruction accuracy within
each narrow frequency band (Figs.~\ref{fig:frequency} and \freqpower).  Activity
at lower frequencies ($\delta$, $\theta$, $\alpha$, and $\beta$) tended to be
reconstructed better than high-frequency patterns ($\gamma_L$ and $\gamma_H$),
with reconstruction accuracy peaking in the $\alpha$ band.  Overall, these
results indicate that our approach is able to accurately recover information
within the 2--100 Hz range, although those reconstructions are most accurate for
low-frequency or broadband patterns.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/frequency}
  \caption{\textbf{Reconstruction quality across all electrodes in two
      ECoG datasets for each frequency band.} \textbf{A. Distributions of correlations
      between observed versus reconstructed activity by electrode, for
      each frequency band in Dataset 1.}  The across-patient
    distribution (left jitter barplot) reflects
    reconstruction accuracy (correlation) using a correlation model
    learned from all but one patient's data, and then applied to that
    held-out patient's data.  The within-patient distribution (right
    jitter barplot in lighter color)
    reflects performance using a correlation model learned from the same
    patient who contributed the to-be-reconstructed electrode, colored
    by frequency and includes the raw voltages displayed in
    Fig.~\ref{fig:corrmap}A in gray.
    \textbf{B.~Statistical summary of across-patient reconstruction
      quality by electrode for each frequency band in Dataset 1.} In the upper triangles of each
    map, warmer colors (positive t-values) indicate that the
    distribution of
    reconstruction accuracy for the frequency band in a given row
    yielded was greater than the frequency band in the given
    column. Cooler colors (negative t-values) indicate that the
    frequency band in the given row yielded lower reconstruction
    accuracy than the frequency band in the given column. The lower
    triangles of each map denote the corresponding p-values for the
    t-tests. The diagonal entries display the average
    reconstruction accuracy given to each frequency
    band. \textbf{C.~Statistical summary of within-patient reconstruction
      quality by electrode for each frequency band in Dataset 1.}
    This panel displays the within-patient statistical summary,
    in the same format as Panel B.  \textbf{D.~Distributions of correlations
      between observed versus reconstructed activity by electrode, for
      each frequency band in Dataset 2.}  This panel displays
    reconstruction accuracy distributions for each frequency band for
    Dataset 2. \textbf{E.~Statistical summary of
      across-patient reconstruction quality by electrode for each
      frequency band in Dataset 2.} This is the same format as Panel
    B for Dataset 2. \textbf{F.~Statistical summary of
      within-patient reconstruction quality by electrode for each
      frequency band in Dataset 2.}This is the same format as Panel
    C for Dataset 2.}
  \label{fig:frequency}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/density}
  \caption{\textbf{Electrode sampling density by location.}
    \textbf{A.~Electrode sampling density by voxel in Dataset 1.} Each
    voxel is colored by the proportion of total electrodes in the
    dataset that are
    located within a 20~MNI unit radius sphere centered on the given
    voxel.  \textbf{B.~Electrode sampling density by voxel in Dataset
      2.}  This panel displays the sampling density map for Dataset 2,
    in the same format as Panel A.  \textbf{C.~Correspondence in
      sampling density by voxel across Datasets 1 and 2.}  The
    two-dimensional histogram displays the by-voxel densities in the
    two Datasets, and the one-dimensional histograms display the
    proportions of voxels in each dataset with the given density
    value.  The correlation reported in the panel is across voxels in
    the 4~mm$^3$ MNI brain.}
  \label{fig:density}
\end{figure}

A basic assumption of our approach (and of most prior ECoG work) is that
electrode recordings are most informative about the neural activity near the
recording surface of the electrode.  But if we consider that activity patterns
throughout the brain are meaningfully correlated, are there particular
implantation locations that, if present in a patient's brain, yield especially
high reconstruction accuracies throughout the rest of the brain?  For example,
one might hypothesize that brain structures that are heavily interconnected with
many other structures could be more informative about full-brain activity
patterns than comparatively isolated structures.  To test this hypothesis, we
computed the average reconstruction accuracy across all of each patient's
electrodes (using our across-patients cross validation test; black histograms in
Fig.~\ref{fig:corrmap}A and B).  We first labeled each patient's electrodes, in
each dataset, with the average reconstruction accuracy for that patient.  In
other words, we assigned every electrode from each patient the same value,
reflecting how well the activity patterns for that patient were reconstructed.
Next, for each voxel in the 4~mm$^3$ MNI brain, we computed the average value
across any electrode (from any patient) that came within 20 MNI units of that
voxel's center.  This yielded an \textit{information score} for each voxel,
reflecting the average reconstruction accuracy across any patients with
electrodes near each voxel-- where the averages were weighted to reflect
patients who had more electrodes implanted near that location. We created a
single map of these information scores for each dataset, highlighting regions
that are especially informative about activity in \textit{other} brain areas
(Fig.~\ref{fig:informap}A and B).  Despite task and patient differences across
the two datasets, we nonetheless found that the maps of the most promising
implantation targets derived from both datasets were similar (voxelwise
correlation between information scores across the two datasets: $r = 0.18, p <
10^{-10}$).  While the correspondence between the two maps was imperfect, our
finding that there were some commonalities between the two maps lends support to
the notion that different brain areas are differently informative about
full-brain activity patterns.  We also examined the intersection between the top
10\% most informative voxels across the two datasets (gray areas in
Fig.~\ref{fig:informap}C, networks shown in Fig.~\ref{fig:networks}A (All)).
Supporting the notion that structures that are highly interconnected with the
rest of the brain might be especially good targets for implantation, this
intersecting set of voxels with the highest information scores included major
portions of the dorsal attention network (e.g., inferior parietal lobule,
precuneus, inferior temporal gyrus, thalamus, and striatum) as well as some
portions of the default mode network (e.g., angular gyrus) that are highly
interconnected with a large proportion of the brain's gray matter~\citep[e.g.,
][]{TomaVolk11}.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/informap}
  \caption{\textbf{Most informative electrode locations.}
    \textbf{A. Dataset 1 information score by voxel.} The voxel colors
    reflect the weighted average reconstruction accuracy across all
    electrodes from any patients with at least one electrode within 20
    MNI units of the given voxel.  \textbf{B. Dataset 2 information
      score by voxel.}  This panel is in the same format as Panel A.
    In both panels the contours indicate the intersections between the
    top 10\% most informative voxels in each map (also see
    Fig.~\networks Panels A.-C. All for networks within this region).  \textbf{C. Intersection.}
    Gray areas indicate the intersections between the
    top 10\% most informative voxels in each map and projected onto the cortical surface~\citep{CombEtal19}. \textbf{D. Correspondence in information
      scores by voxel across Datasets 1 and 2.}  Same format as
    Figure~\ref{fig:density}C.}
  \label{fig:informap}
\end{figure}

We also wondered whether the map of information scores might vary as a function
of the spectral components of the activity patterns under consideration.  We
computed analogous maps of information scores for each individual frequency
band. Across Datasets 1 and 2 (with the exception of $\alpha$ band activity), we
observed reliable positive correlations between the voxel-by-voxel maps of
information scores ($\delta$: $r = 0.09, p < 10^{-57}$; $\theta$: $r = 0.24, p <
10^{-60}$; $\alpha$: $r = -0.03, p < 0.001$, $\beta$: $r = 0.02, p - 0.0011$;
$\gamma_L$: $r = 0.1, p < 10^{-67}$; $\gamma_H$: $r = 0.03, p < 10^{-7}$;
broadband: $r = 0.21, p < 10^{-297})$.

To gain additional insight into which regions were most informative about
full-brain activity patterns at different frequency ranges, we next computed
(for each frequency range) the intersection of the top 10\% highest information
scores across the maps for Datasets 1 and 2 (analogous to our approach in
Fig.~\ref{fig:informap}C). This yielded a single map of the (reliably) most
informative locations for each frequency range we examined. We then carried out
two \textit{post hoc} analyses on each of these maps to better characterize the
underlying structural and functional properties of each set of regions we
identified as being particularly informative about one or more neural patterns.

>>>>

\section*{Approach} The SuperEEG approach to inferring high temporal resolution
full-brain activity patterns is outlined and summarized in
Figure~\ref{fig:methods}. We describe (in this section) and evaluate (in
\textit{Results}) our approach using a two large previously collected datasets
comprising multi-session intracranial recordings. Dataset 1 comprises
multi-session recordings taken from 6876 electrodes implanted in the brains of
88 epilepsy patients~\citep{SedeEtal03, SedeEtal07a, SedeEtal07b, MannEtal11,
MannEtal12}.  Each recording session lasted from 0.2--3~h (total recording time:
0.3--14.2~h; Fig.~\suppstats E).  During each recording session, the patients
participated in a free recall list learning task, which lasted for up to
approximately 1~h.  In addition, the recordings included ``buffer'' time (the
length varied by patient) before and after each experimental session, during
which the patients went about their regular hospital activities (confined to
their hospital room, and primarily in bed).  These additional activities
included interactions with medical staff and family, watching television,
reading, and other similar activities.  For the purposes of the Dataset 1
analyses presented here, we aggregated all data across each recording session,
including recordings taken during the main experimental task as well as during
non-experimental time.  We used Dataset 1 to develop our main SuperEEG approach,
and to examine the extent to which SuperEEG might be able to generate
task-general predictions.  Dataset 2 comprised multi-session recordings from
14860 electrodes implanted in the brains of 131 epilepsy
patients~\citep{EzzyEtal17, HoraEtal17, KragEtal17, KuceEtal17, LinEtal17,
SoloEtal18, WeidEtal18, EzzyEtal18, KuceEtal18}.  Each recording session lasted
from 0.4--2.2~h (total recording time: 0.4--6.6~h; Fig.~\suppstats K).  Whereas
Dataset 1 included recordings taken as the patients participated in a variety of
activities, Dataset 2 included recordings taken as each patient performed each
of two specific experimental memory tasks: a random word list free recall task
(Experiment 1) and a categorized word list free recall task (Experiment 2).  We
used Dataset 2 to further examine the ability of SuperEEG to generalize its
predictions within versus across tasks.  Figure~\suppstats~provides additional
information about both datasets.

@@

We first applied fourth order Butterworth notch filters to remove 60 Hz ($\pm$
.5 Hz) line noise from every recording (from every electrode). Next, we
downsampled the recordings (regardless of the original sample rate) to 250 Hz.
This downsampling step served to both normalize for differences in sampling
rates across patients and to ease the computational burden of our subsequent
analyses.  We then excluded any electrodes that showed putative epileptiform
activity. Specifically, we excluded from further analysis any electrode that
exhibited a maximum kurtosis of 10 or greater across all of that patient's
recording sessions.  We also excluded any patients with fewer than 2 electrodes
that passed this criteria, as the SuperEEG algorithm requires measuring
correlations between 2 or more electrodes from each patient.  For Dataset 1,
this yielded clean recordings from 4168 electrodes implanted throughout the
brains of 67 patients (Fig.~\ref{fig:methods}A, colored dots); for Dataset 2,
this yielded clean recordings from 5023 electrodes implanted in 78 patients.
Each individual patient contributed electrodes from a limited set of brain
locations, which we localized in a common space~\citep[MNI152;][]{GrabEtal06};
an example Dataset 1 patient's 54 electrodes that survived the kurtosis
thresholding procedure are highlighted in black and red
(Fig.~\ref{fig:methods}A).

@@

We designed our approach to be agnostic to electrode impedances, as electrodes
that do not exist do not have impedances.  Therefore our algorithm recovers
voltages in standard deviation ($z$-scored) units rather than attempting to
recover absolute voltages. (This property reflects the fact that
$\hat{K}_{\beta_s, \alpha_s}$ and $\hat{K}_{\alpha_s, \alpha_s}$ are correlation
matrices rather than covariance matrices.)  Also, we note that
Equation~\ref{eqn:reconstruction} requires computing a $T$ by $T$ matrix, which
can become computationally intractable when $T$ is very large (e.g., an example
patient in Dataset 1, $T = 51147$; also see Fig.~\suppstats, Panels E and
K). However, because Equation~\ref{eqn:reconstruction} is time invariant, we may
compute $Y_{s,k,\beta_s}$ in a piecewise manner by filling in $Y_{s,k,\beta_s}$
one row at a time (using the corresponding samples from $Y_{s, k, \alpha_s}$).

@@

%correlations by brain area, distribution of correlations
\begin{figure}
  \centering \includegraphics[width=\textwidth]{figs/corrmap}
  \caption{\textbf{Reconstruction accuracy across all electrodes in two ECoG
  datasets.}  \textbf{A. Distributions of correlations between observed versus
  reconstructed activity by electrode, for Dataset 1.}  The across-patient
  distribution (black) reflects reconstruction accuracy (correlation) using a
  correlation model learned from all but one patient's data, and then applied to
  that held-out patient's data.  The within-patient distribution (gray) reflects
  performance using a correlation model learned from the same patient who
  contributed the to-be-reconstructed electrode. \textbf{B. Distributions of
  correlations for Dataset 2.}  This panel is in the same format as Panel A, but
  reflects results obtained from Dataset 2.  The histograms aggregate data
  across both Dataset 2 experiments; for results broken down by experiment see
  Figure~\perexptaskreconseparated. \textbf{C.--D.  Reconstruction accuracy by
  location.} The colors denote the average across-session correlations, using
  the across-patient correlation model, between the observed and reconstructed
  activity at the given electrode location projected to the cortical
  surface~\citep{CombEtal19}.  Panel C displays the map for Dataset 1 and Panel
  D displays the map for Dataset 2.} \label{fig:corrmap}
\end{figure}

@@

Although both datasets we examined provide good full-brain coverage (when
considering data from every patient), electrodes were not sampled uniformly
throughout the brain.  For example, electrodes are more likely to be implanted
in regions like the medial temporal lobe (MTL), and are rarely implanted in
occipital cortex (Fig.~\ref{fig:density}A, B). Separately for each dataset, for
each voxel in the 4~mm$^3$ voxel MNI152 brain, we computed the proportion of
electrodes in the dataset that were contained within a 20 MNI unit radius sphere
centered on that voxel.  We defined the \textit{density} at that location as
this proportion. Across Datasets 1 and 2, the electrode placement densities were
similar (correlation by voxel: $r = 0.6, p < 10^{-10}$).  We wondered whether
regions with good covererage might be associated with better reconstruction
accuracy. For example, Figures~\ref{fig:density}A and B indicate that many
electrodes in the MTL (which tends to be relatively densely sampled) have
relatively high reconstruction accuracy, and occipital electrodes (which tends
to be relatively sparsely sampled) tend to have relatively low reconstruction
accuracy.  To test whether this held more generally across the entire brain, for
each dataset we computed the electrode placement density for each electrode from
each patient (using the proportion of \textit{other} patients' electrodes within
20 MNI units of the given electrode).  We then correlated these density values
with the across-patient reconstruction accuracies for each electrode.  We found
no reliable correlation between reconstruction accuracy and density for Dataset
1 ($r = 0.05, p = 0.70$) and a reliable negative correlation for Dataset 2 ($r =
-0.21, p = 0.05$).  This indicates that the reconstruction accuracies we
observed are \textit{not} driven solely by sampling density, but rather may also
reflect higher order properties of neural dynamics such as functional
correlations between distant voxels~\citep{BetzEtal17b}.

Prior work in humans and animals has shown that the spatial profile of the local
field potential differs by frequency band~\citep[e.g., with respect to volume
conductance properties and contribution to the local field
potential;][]{BuzsEtal12, FrieEtal07, CronEtal11}.  For example, lower frequency
components of the local field potential tend to have higher power and extend
further in space than high-frequency components~\citep[e.g., ][]{MillEtal07,
MannEtal09}.  We therefore wondered whether the reconstructions we observed
might be differently weighting or considering the contributions of activity at
different frequency bands.  We therefore examined a range of frequency bands
($\delta$: 2--4 Hz; $\theta$: 4--8 Hz; $\alpha$: 8--12 Hz; $\beta$: 12--30 Hz;
$\gamma_L$: 30--60 Hz; and $\gamma_H$: 60--100 Hz), along with a measure of
broadband power.  We defined broadband power as the mean height of a linear
robust regression fit in log-log space to the order 4 Morelet wavelet-computed
power spectrum at 50 log-spaced frequencies from from 2--100
Hz~\citep{MannEtal09}. We used second-order Butterworth bandpass filters to
compute the activity patterns within each narrow frequency band.  We then
repeated our within-subject and across-subject cross-validated reconstruction
accuracy tests (analogous to Fig.~\ref{fig:corrmap}) separately for each
frequency band (Fig.~\ref{fig:frequency}).  (We also carried out a similar
analysis on the Hilbert transform-computed spectral power within each narrow
band; see Fig.~\freqpower.)  Across both datasets, we found that our approach is
best at reconstructing patterns of broadband activity (right-most bars in
Figs.~\ref{fig:frequency}A and D), a correlate of population firing
rate~\citep{MannEtal09}.  We also achieved good reconstruction accuracy within
each narrow frequency band (Figs.~\ref{fig:frequency} and \freqpower).  Activity
at lower frequencies ($\delta$, $\theta$, $\alpha$, and $\beta$) tended to be
reconstructed better than high-frequency patterns ($\gamma_L$ and $\gamma_H$),
with reconstruction accuracy peaking in the $\alpha$ band.  Overall, these
results indicate that our approach is able to accurately recover information
within the 2--100 Hz range, although those reconstructions are most accurate for
low-frequency or broadband patterns.

\begin{figure}
  \centering \includegraphics[width=\textwidth]{figs/frequency}
  \caption{\textbf{Reconstruction accuracy across all electrodes in two ECoG
  datasets for each frequency triangles.} \textbf{A. Distributions of
  correlations between observed versus reconstructed activity by electrode, for
  each frequency band in Dataset 1.}  Each color denotes a different frequency
  range. Within each color group, the darker dots and bar on the left display
  the distribution (and mean) across-patient reconstruction accuracies
  (analogous to the black histograms in Fig.~\ref{fig:corrmap}).  The lighter
  dots and bar on the right display the distribution (and mean) within-patient
  reconstruction accuracies (analogous to the gray histograms in
  Fig.~\ref{fig:corrmap}). To facilitate visual comparison with the
  frequency-specific results, the leftmost bars (gray) re-plot the histograms in
  Fig.~\ref{fig:corrmap}A. \textbf{B.~Statistical summary of across-patient
  reconstruction accuracy by electrode for each frequency band in Dataset 1.} In
  the upper triangles of each map, warmer colors (positive $t$-values) indicate
  that the distribution of reconstruction accuracy for the frequency band in a
  given row yielded was greater than the frequency band in the given column.
  Cooler colors (negative $t$-values) indicate that the frequency band in the
  given row yielded lower reconstruction accuracy than the frequency band in the
  given column. The lower triangles of each map denote the corresponding
  $p$-values for the $t$-tests. The diagonal entries display the average
  reconstruction accuracy within each frequency band. \textbf{C.~Statistical
  summary of within-patient reconstruction accuracy by electrode for each
  frequency band in Dataset 1.} This panel displays the within-patient
  statistical summary, in the same format as Panel B.  \textbf{D.~Distributions
  of correlations between observed versus reconstructed activity by electrode,
  for each frequency band in Dataset 2.}  This panel displays reconstruction
  accuracy distributions for each frequency range for Dataset 2.
  \textbf{E.--F.~Statistical summaries of across-patient and within-patient
  reconstruction accuracy by electrode for each frequency band in Dataset 2.}
  These panels are in the same as Panels B and C, but display results from
  Dataset 2.} \label{fig:frequency}
\end{figure}

\begin{figure}
  \centering \includegraphics[width=\textwidth]{figs/density}
  \caption{\textbf{Electrode sampling density by location.} \textbf{A.~Electrode
  sampling density by voxel location in Dataset 1.} Each voxel is colored by the
  proportion of total electrodes in the dataset that are located within a 20~MNI
  unit radius sphere centered on the given voxel.  \textbf{B.~Electrode sampling
  density by voxel location in Dataset 2.}  This panel displays the sampling
  density map for Dataset 2, in the same format as Panel A.
  \textbf{C.~Correspondence in sampling density by voxel location across
  Datasets 1 and 2.}  The two-dimensional histogram displays the per-voxel
  sampling densities in the two Datasets, and the one-dimensional histograms
  display the proportions of voxels in each dataset with the given density
  value.  The correlation reported in the panel is across voxels in the 4~mm$^3$
  MNI152 brain.} \label{fig:density}
\end{figure}

A basic assumption of our approach (and of most prior ECoG work) is that
electrode recordings are most informative about the neural activity near the
recording surface of the electrode.  But if we consider that activity patterns
throughout the brain are meaningfully correlated, are there particular
implantation locations that, recorded from in a given patient's brain, yield
especially high reconstruction accuracies throughout the rest of their brain?
For example, one might hypothesize that brain structures that are heavily
interconnected with many other structures could be more informative about
full-brain activity patterns than comparatively isolated structures.  To test
this hypothesis, we computed the average reconstruction accuracy across all of
each patient's electrodes (using our across-patients cross validation test;
black histograms in Fig.~\ref{fig:corrmap}A and B).  We first labeled each
patient's electrodes, in each dataset, with the average reconstruction accuracy
for that patient.  In other words, we assigned every electrode from each patient
the same value, reflecting how well the activity patterns for that patient were
reconstructed. Next, for each voxel in the 4~mm$^3$ MNI brain, we computed the
average value across any electrode (from any patient) that came within 20 MNI
units of that voxel's center.  This yielded an \textit{information score} for
each voxel, reflecting the average reconstruction accuracy across any patients
with electrodes near each voxel-- where the averages were weighted to reflect
patients who had more electrodes implanted near that location. We created a
single map of these information scores for each dataset, highlighting regions
that are especially informative about activity in \textit{other} brain areas
(Fig.~\ref{fig:informap}A and B).  Despite task and patient differences across
the two datasets, we nonetheless found that the maps of the most promising
implantation targets derived from both datasets were correlated (voxel-wise
correlation between information scores across the two datasets: $r = 0.18, p <
10^{-10}$).  Our finding that there were some commonalities between the two
datasets' maps lends support to the notion that different brain areas are
(reliably) differently informative about full-brain activity patterns.  We also
examined the intersection between the top 10\% most informative voxels across
the two datasets (gray areas in Fig.~\ref{fig:informap}C, networks shown in
Fig.~\ref{fig:networks}A, top row). Supporting the notion that structures that
are highly interconnected with the rest of the brain are most informative about
full-brain activity patterns, the intersecting set of voxels with the highest
information scores included major portions of the dorsal attention network
(e.g., inferior parietal lobule, precuneus, inferior temporal gyrus, thalamus,
and striatum) as well as some portions of the default mode network (e.g.,
angular gyrus) that are highly interconnected with a large proportion of the
brain's gray matter~\citep[e.g.,][]{TomaVolk11}.

\begin{figure}
  \centering \includegraphics[width=\textwidth]{figs/informap}
  \caption{\textbf{Most informative recording locations.} \textbf{A. Dataset 1
  information scores by voxel.} The voxel colors reflect the weighted average
  reconstruction accuracy across all electrodes from any patients with at least
  one electrode within 20 MNI units of the given voxel.  \textbf{B. Dataset 2
  information scores by voxel.}  This panel is in the same format as Panel A.
  \textbf{C. Intersection.} Gray areas indicate the intersections between the
  top 10\% most informative voxels in each map and projected onto the cortical
  surface~\citep{CombEtal19}. \textbf{D. Correspondence in information scores by
  voxel across Datasets 1 and 2.}  The correlation reported in the Panel is
  between the per-voxel information scores across Datasets 1 and 2.}
  \label{fig:informap}
\end{figure}

We also wondered whether the map of information scores might vary as a function
of the spectral components of the activity patterns under consideration.  We
computed analogous maps of information scores for each individual frequency
range. Across Datasets 1 and 2 (with the exception of $\alpha$ band activity),
we observed reliable positive correlations between the voxel-by-voxel maps of
information scores ($\delta$: $r = 0.09, p < 10^{-57}$; $\theta$: $r = 0.24, p <
10^{-60}$; $\alpha$: $r = -0.03, p < 0.001$, $\beta$: $r = 0.02, p - 0.0011$;
$\gamma_L$: $r = 0.1, p < 10^{-67}$; $\gamma_H$: $r = 0.03, p < 10^{-7}$;
broadband: $r = 0.21, p < 10^{-297})$.

To gain additional insight into which regions were most informative about
full-brain activity patterns at different frequency ranges, we next computed
(for each frequency range) the intersection of the top 10\% highest information
scores across the maps for Datasets 1 and 2 (analogous to our approach in
Fig.~\ref{fig:informap}C). This yielded a single map of the (reliably) most
informative locations, for each frequency range we examined. We then carried out
\textit{post hoc} analyses on each of these maps to better characterize the
underlying structural and functional properties of each set of regions we
identified as being particularly informative about one or more neural patterns.

A growing body of neuroscientific research is concerned with characterizing the
\textit{parcellations} of anatomical and functional brain networks~\citep[for
review see][]{ZaleEtal10, ArslEtal18}. The dominant approaches entail obtaining
a full-brain connectivity matrix using either diffusion tensor imaging to
identify the brain's network of white matter connections, or functional
connectivity (typically applied to resting state data) to correlate the patterns
of activity exhibited by different brain structures.  One can then apply graph
theoretic approaches to assign each brain structure (typically a single fMRI
voxel) to one or more networks~\citep[for review see][]{BullSpor09}. The result
is a set of distinct (or partially overlapping) brain ``networks'' that may be
further examined to elucidate their potential functional role.  We overlaid a
well-cited seven-network parcellation map identified by \cite{YeoEtal11} onto
the maps of brain locations that were most informative about each type of neural
pattern.  For each of these information maps, we computed the proportion of
voxels in the most informative brain regions that belonged to each of the seven
networks identified by \cite{YeoEtal11}; Figure~\ref{fig:networks}D. We found
that the regions we identified as being most informative about different neural
patterns varied markedly with respect to which functional networks they belonged
to (Fig.~\ref{fig:networks}A, B).

\begin{figure}
  \centering \includegraphics[width=\textwidth]{figs/networks}
  \caption{\textbf{Most informative recording locations by frequency range.}
  \textbf{A.~Intersections between information score maps by frequency range.}
  The regions indicated in each row depict the intersection between the top 10\%
  most informative locations across Datasets 1 and 2.  \textbf{B.~Network
  memberships of the most informative brain regions.}  The pie charts display
  the proportions of voxels in each region that belong to the seven networks
  identified by \cite{YeoEtal11}.  The relative sizes of the charts for each
  frequency range reflct the average across-subject reconstruction accuracies
  (Fig.~\ref{fig:corrmap}A, D).  The voxels in Panel A are colored according to
  the same network memberships.  \textbf{C.~Neurosynth terms associated with the
  most informative brain regions, by frequency range.}  The lists in each row
  display the top five neurosynth terms~\citep{RubiEtal17} decoded for each
  region.  \textbf{D.~Network parcellation map and legend.}  The parcellation
  defined by \cite{YeoEtal11} is displayed on the inflated brain maps.  The
  colors and network labels serve as a legend for Panels A and B.
  \textbf{E.~Combined map of the most informative brain regions.}  The map
  displays the union of the most informative maps in Panel A, colored by
  frequency range.  The labels also serve as a legend for Panel C.}
  \label{fig:networks}
\end{figure}
